### 2018-08-02 README.Rmd
readme

Central to `taxald` design is to create a *local* database of all avialable taxonomic authority data that we can query quickly, even when working with tens of thousands of species. The second key feature of `taxald` design is to return queries from each authority using a *consistent* and convenient table structure, facilitating queries that compare, combine, or work across names from multiple authorities.

@@

@@

```{r}
library(taxald)
```

```{r eval=FALSE}
create_taxadb()
```

@@

```{r}
library(tictoc) # let's display timing of queries for reference
```

>>>>

Central to `taxald` design is to create a *local* database of all available taxonomic authority data that we can query quickly, even when working with tens of thousands of species. The second key feature of `taxald` design is to return queries from each authority using a *consistent* and convenient table structure, facilitating queries that compare, combine, or work across names from multiple authorities.

@@

```{r}
library(taxald)
library(tictoc) # let's display timing of queries for reference
```

@@

```{r eval = TRUE, message=FALSE}
tic()
create_taxadb()
toc()
```

@@
